aircraft-pfp

### 2024-08-22 examples/aircraft-insitu.Rmd
add plots to articles

---
title: "aircraft-flask"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircraft-pfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "aircraft-flask"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r aggregatingdata, eval = T}
df2 <- obs_agg(df, cols =  c("year",
                             "month",
                             "day",
                             "hour",
                             "minute",
                             "second",
                             "time",
                             "time_decimal",
                             "value",
                             "latitude",
                             "longitude",
                             "altitude_final",
                             "elevation",
                             "intake_height",
                             # "gps_altitude",
                             # "pressure",
                             # "pressure_altitude",
                             # "u", "v", "temperature",
                             "type_altitude"))
```
## Add local time

@@

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftflask.png?raw=true)

>>>>

---
title: "aircraft-insitu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircraft-insitu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "aircraft-insitu"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r aggregatingdata, eval = T}
df2 <- obs_agg(df, cols =  c("year",
                             "month",
                             "day",
                             "hour",
                             "minute",
                             "second",
                             "time",
                             "time_decimal",
                             "value",
                             "latitude",
                             "longitude",
                             "altitude_final",
                             "elevation",
                             "intake_height",
                             "gps_altitude",
                             "pressure",
                             "pressure_altitude",
                             "u", "v", "temperature",
                             "type_altitude"))
```
## Add local time

@@

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftinsitu.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircrafinsitu.png?raw=true)

### 2024-08-22 examples/aircraft-pfp.Rmd
add plots to articles

---
title: "aircraft-insitu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircraft-insitu}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "aircraft-insitu"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftinsitu.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircrafinsitu.png?raw=true)

>>>>

---
title: "aircraft-pfp"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{aircraft-pfp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "aircraft-pfp"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = FALSE,
                  verbose = T)

@@

```{r obs_plotsave, fig.width=7, fig.height=5, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_aircraftpfp.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftpfp.png?raw=true)

```{r savesf, fig.width=7, fig.height=5, eval = T, echo = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_aircraftpfp_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

```{r sf, fig.width=7, fig.height=5, eval = F}
library(sf)
x <- st_as_sf(df3, coords = c("longitude", "latitude"), crs = 4326)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
```

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftpfp_map.png?raw=true)
